Biden More Favorable Among Female, Black, Asian, Hispanic, Middle Eastern, and Non-gun Owning Voters in the 2020 US Presidential Election

### 2024-03-16 paper/paper.qmd
Update paper with citations

The language and environment used for this analysis is R [@citeR], alongside the tidyverse [@tidyverse], dataverse [@dataverse], arrow [@arrow], rstanarm [@rstanarm], knitr [@knitr], here [@here], ggplot2 [@ggplot2], scales [@scales], modelsummary [@modelsummary], and marginaleffects [@marginaleffects] packages.

>>>>

The language and environment used for this analysis is `R` [@citeR], alongside the `tidyverse` [@tidyverse], `dataverse` [@dataverse], `arrow` [@arrow], `rstanarm` [@rstanarm], `knitr` [@knitr], `here` [@here], `ggplot2` [@ggplot2], `scales` [@scales], `modelsummary` [@modelsummary], and `marginaleffects` [@marginaleffects] packages.
